Inference methods comparison for the simplified Naomi model

### 2023-01-30 src/naomi-simple_compare/comparison.Rmd
aghq hypers debugged so that we do have samples, still need to work out an approach for what to do when k = 1
Update naomi-simple_compare so that it includes a histogram of the first entry of beta_rho -- the parameter that I'm testing Laplace marginals on

```{r}
histogram_plot("beta_anc_rho")
```

@@

```{r}
(big_ks <- ks_summary %>%
  filter(`KS(aghq, tmbstan)` > 0.5, `KS(TMB, tmbstan)` > 0.5) %>%
  pull(Parameter))
```

>>>>

```{r}
histogram_plot("beta_rho", i = 1)
histogram_plot("beta_anc_rho")
```

@@

```{r}
(big_ks <- ks_summary %>%
  filter(`KS(aghq, tmbstan)` + `KS(TMB, tmbstan)` > 0.5) %>%
  pull(Parameter))
```
